---
title: "RIsk Analysis"
author: "Oracy Martos"
date: "November 25, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Risk Analysis

Para esta análise, vamos usar um conjunto de dados German Credit Data, já devidamente limpo e organizado para a criação do modelo preditivo.

Todo o projeto será descrito de acordo com suas etapas.

## Step 1 - Collecting Data

# Set Directory
setwd("/home/oracy/Documents/DSA_Projetos/DSA_Projetos/Big Data Analytics com R e Microsoft Azure Machine Learning/4.Analise de Risco de Credito")
getwd()

```{r coleta}
# Data gathering
# Loading the dataset into a dataframe
df <- read.csv('credit_dataset.csv', header = TRUE, sep = ',')
head(df)
str(df)
```


## Step 2 - Normalizando os Dados

```{r normalizando}
# Loading my library
source('utils.R')

# Normalizing the variables
numeric.vars <- c("credit.duration.months", "age", "credit.amount")
df <- scale.features(df, numeric.vars)

# Factor type variables
factor.vars <- c('credit.rating', 'account.balance', 'previous.credit.payment.status',
                 'credit.purpose', 'savings', 'employment.duration', 'installment.rate',
                 'marital.status', 'guarantor', 'residence.duration', 'current.assets',
                 'other.credits', 'apartment.type', 'bank.credits', 'occupation', 
                 'dependents', 'telephone', 'foreign.worker')

df <- to.factors(df, factor.vars)

```


## Step 3 - Splitting data in training and testing - 60:40 ratio
# Font: https://cran.r-project.org/web/packages/dataPreparation/vignettes/train_test_prep.html


```{r treinamento}
nrow(df)
index <- sample(1:nrow(df), 0.6 * nrow(df))
df_train <- df[index,]
df_test <- df[-index,]
length(df_train)
length(df_test)
```


## Step 4 - Feature Selection
# Font: https://machinelearningmastery.com/feature-selection-with-the-caret-r-package/
# Font: https://machinelearningmastery.com/feature-selection-with-the-caret-r-package/

```{r performance}
#install.packages('caret')
#install.packages('e1071', dependencies = TRUE)
#install.packages('randomForest')
library(caret)
library(randomForest)

# Running the function
rfe.results <- feature.selection(feature.vars = df_train[,-1],
                                 class.var = df_train[,1])

# Viewing Results
rfe.results
varImp(rfe.results)
predictors(rfe.results)
plot(rfe.results, type = c("g","o"))

```


## Step 5 - Creating and Evaluating the Model
 
 
 
```{r avaliando}
#install.packages('ROCR')
library(ROCR)
# Biblioteca de utilitários para construção de gráficos
source('plot_utils.R')

## separate feature and class variables
test.feature.var <- df_test[,-1]
test.class.var <- df_test[,1]

# Building a Logistic Regression Model
lm.init <- 'credit.rating ~ .'
lm.init <- as.formula(lm.init)
lr.model <- glm(formula = lm.init, data = df_train, family = "binomial")
  
# Viewing the template
summary(lr.model)
any(is.na(df))

# Testing the Model in Test Data
lr.predictions <- predict(lr.model, df_test, type = "response")
lr.predictions <- round(lr.predictions)

# Evaluating the model
confusionMatrix(table(data = lr.predictions, reference = test.class.var), positive = '1')
```


## Step 6 - Optimizing Model

```{r otimizando}
## Feature selection
formula <- 'credit.rating ~ .'
formula <- as.formula(formula)
control <- trainControl(method = "repeatedcv", number = 10, repeats = 2)
model <- train(formula, data = df_train, method = "glm", trControl = control)
importance <- varImp(model, scale = FALSE)
plot(importance)

# Building the model with the selected variables
newFormula <- "credit.rating ~ account.balance + credit.purpose + previous.credit.payment.status + savings + credit.duration.months"
newFormula <- as.formula(newFormula)
lrNewModel <- glm(formula = newFormula, data = df_train, family = "binomial")

# Viewing the template
summary(lrNewModel)

# Testing the Model in Test Data
lrNewPrediction <- predict(lrNewModel, df_test, type = "response")
lrNewPrediction <- round(lrNewPrediction)

# Evaluating the model
confusionMatrix(table(data = lrNewPrediction, reference = test.class.var), positive = '1')
```

## Step 7 - ROC Curve e Final Model Evaluation

```{r curva}
# Avaliando a performance do modelo
# Creating ROC Curves
lrModelBest <- lr.model
lrPredictionValue <- predict(lrModelBest, test.feature.var, type = "response")
predictions <- prediction(lrPredictionValue, test.class.var)
par(mfrow = c(1, 2))
plot.roc.curve(predictions, title.text = "ROC Curve")
plot.pr.curve(predictions, title.text = "Precision/Recall Curve")
```